### 2013-12-03 proposal/proposal/chapter3.tex
changes

@@

\subsection{The Architecture}

@@

\emph{1) Web services} are rational entities\footnote{The term
rational is used here in the sense that web services are utility
maximizers} providing services to end users. They aim to maximize
their individual income by receiving enough requests from end
users. In order to increase their revenue, web services seek for
more tasks if they have the capacity and throughput to do so. Web
services can join communities to have better efficiency by
collaborating with others, to have access to higher market share,
and to have opportunity of receiving a bigger task pool from end
users. Throughout this proposal, in
our equations, we refer to web services as $ws$ and to the set of
web services hosted by a given community as $C$. To simplify the
notation, sometimes we simply write $ws$ instead of $ws \in C$ to
go through the elements $ws$ of the set $C$.

@@

Figure \ref{fig_community} represents the architecture of web service communities. The communities are essentially an abstract model of web services. They aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols as web services. Web services join communities to increase their utility by having a larger market share and task pool. Community coordinators or master web services are responsible for community development, managing membership requests from web services and distributing user tasks among the community members. Community coordinators try to attract quality web services and keep the community as stable and productive as possible to gain better reputation and user satisfaction which results in having a higher market share for the community. The way the web services reside inside communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.

\begin{figure*}[!t]
\centerline{\includegraphics[width=15cm]{Figures/community.eps}}
\caption{Architecture of Web Service communities}
\label{fig_community}
\end{figure*}

@@

\subsection{Task distribution}

As mentioned in section \ref{webservice-communities}, communities are robust service providers with well established market share and reputation. By maintaining their reputation and performance, they attract  end users which choose them as service providers to perform their tasks. The community master is characterized by a request rate $(R_C)$ from users. Each web service comes with a given QoS ($QoS_{ws}$) from which the throughput $Th_{ws}$ is excluded. Throughput is the average rate of tasks a web service can perform per time unit. Its exclusion from $QoS_{ws}$ allows us to build our analysis on the particular value of $Th_{ws}$. Thus, web services perform tasks with an average output quality of $QoS_{ws}$ and a throughput rate of $Th_{ws}$.

@@

The communities and web services earn revenue by performing tasks. The total gain is function of quality ($QoS_{ws}$) and throughput ($Th_{ws}$) of tasks being performed. As mentioned in section \ref{ws_parameters}, $QoS_{ws}$ is obtained by a certain aggregation function of the parameters considered in Table \ref{qosws}. We have adopted a linear equal weight average over all QoS parameters listed in table \ref{qosws} excluding the $Throughput$ and $Cost$ parameters. A community has the option to weigh specific QoS parameters depending on the expectations of their clients.

@@

%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Example 1}
\label{example_1}
\centering
\begin{tabular}{c c c c}
\hline
$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
\hline
1 & 0.8 & 4 & 3.2\\
2 & 0.8 & 5 & 4.0\\
3 & 0.8 & 3 & 2.4\\
\hline
\end{tabular}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Example 2}
\label{example_2}
\centering
\begin{tabular}{c c c c}
\hline
$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
\hline
1 & 0.8 & 5 & 4.0\\
2 & 0.7 & 6 & 4.2\\
3 & 0.7 & 4 & 2.8\\
\hline
\end{tabular}
\end{table}

@@

In the first example,  we present the case of a community with $R_C =10 $, and three web services, each having different $QoS_{ws}$ and $Th_{ws}$ values as listed in table \ref{example_1}. The worth of a community is calculated based on $Out(C)$ equation (\ref{out_c}) which is the amount of output being generated by the community. The first table  lists the web services with their aggregated $QoS_{ws}$ parameters, their task input rate while working alone, and also their  throughput value $Th_{ws}$. The second table shows all the possible communities and their respective worth. The obtained values suggest that  communities having more web services have better gain and output. However each community needs to  distribute the gain between web services. Sometimes it is impossible to share the gain between all web services in a way that no subset of them would individually gain more if they form their own group. In this example, the value community of ${ws_1}$ and ${ws_2}$ is 7.2, With ${ws_3}$ joining the community the worth increases to 8.0. However there is no way to distribute the value among web services to have  ${ws_1}$ and ${ws_2}$  earning 7.2, and ${ws_3}$ earning at least 2.4, the gain they could earn before joining the community. This fact makes the group unstable. In the second  example, shown in table \ref{example_2}, we even have situations where a web service (${ws_3}$) joining a community ($\left\{ws_1,ws_2\right\}$) decreases the value of community. The reason is, the community is already full and all tasks are almost being distributed and new community with bad quality can degrade the average quality of tasks being done by the community. In both examples, the request of joining of web service ${ws_3}$ should be rejected by the community.

%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Example 3}
\label{example_3}
\centering
\begin{tabular}{c c c c}
\hline
$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $\text{\emph{Input Task Rate}}$\\
\hline
1 & 0.8 & 10 & 5\\
2 & 0.8 & 20 & 5\\
3 & 0.8 & 30 & 5\\
\hline
\end{tabular}
\end{table}

@@

In coalition-formation games, formation of the coalitions is the
most important aspect. The solutions focus on maximizing the
social welfare. For any coalition structure $\pi$, let
$v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$,
which represents the \emph{social welfare}. The solution concepts
in this area deal with finding the maximum value for the social
welfare over all the possible coalition structures $\pi$. There
are $centralized$ algorithms for this end, but these approaches
are generally NP-complete. The reason is that the number of all
possible partitions of the set $N$ grows exponentially with the
number of players in $N$, and the centralized algorithms need to
iterate through all these partitions.
%These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centralized algorithms, where all the complexity. However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}.
In our model, we propose using a distributed algorithm where each
community master and web service can be a decision maker and
decide for its own good. The aim is to find less complex and
distributed algorithms for forming web services
coalitions\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}.
The distributed merge-and-split algorithm in
\cite{DBLP:journals/igtr/AptW09} suits our application very well.
It keeps splitting and merging coalitions to partitions which are
preferred by all the players inside those coalitions.

@@

Finally, in our last experiment, we compare our work with the work in \cite{10.1109/TSC.2012.12} which we call it \emph{High Availability Coalition} method, because of nature of their community valuation function, which focuses on community availability as main consideration. Their community formation model is very different than ours, however we have been very careful to make the experiment environment as fair and similar as possible. We limited our maximum community size by 5 in order to have communities with almost the same size. In their method, they have used web services as backups rather than active collaborative players, and they only get task when the first web service in an ordered chain fails to perform the task. However with recent advancement in cloud and hardware infrastructures availability is less of an issue for web services, and web services are highly available. Part(a) of figure \ref{fig_avail_method} shows our method performs almost performs tasks successfully with rate of three times more than \emph{High Availability Coalition} method because of real cooperative nature and task distribution of our algorithm. This result shows using web services as backups, and not as real collabrative players is a huge waste of web service capability since they have very low chance of getting jobs and its the primary web service (the first in their coordination chain) which does most of the work. The average quality of service of tasks performed is also better since our method considers all quality of service metrics mentioned in table \ref{qosws}. Part(c) shows the availability of community from end user point of view. The \emph {High Availability Coalition} method almost has 100\% uptime since they use web services as backups, so the chance of job failing reduces significantly as community members increase. In our method we have more chance of fail for each web service, however with some subsiding, and hiring a few more web service they can compensate the low chance of failure of web services in our community.

>>>>

In this chapter, we present our coalition model of agent-based web
services within communities\cite{SCC2013efficient}. We start by describing the general
architecture and considered parameters for web services.
Thereafter, problem modeling and formulation will be introduced in
terms of task distribution and community revenue. Web service
cooperative games in different settings will follow along with
some simulation results.

@@

\subsection{Architecture}

@@

\emph{1) Web services} are rational entities that aim to maximize
their utilities by providing high quality services to end users.
They aim to maximize their individual income by receiving enough
requests from end users. In order to increase their revenue, web
services seek for more tasks if they have the capacity and
throughput to do so. Web services can join communities to have
better efficiency by collaborating with others, to have access to
higher market share, and to have opportunity of receiving a bigger
task pool from end users. Throughout this proposal, in our
equations, we refer to web services as $ws$ and to the set of web
services hosted by a given community as $C$. To simplify the
notation, sometimes we simply write $ws$ instead of $ws \in C$ to
go through the elements $ws$ of the set $C$.

@@

Figure 3 represents our revised architecture of web service
communities where tasks are to be distributed among the members
that are interested in forming stable coalitions. As discussed in
Chapter 2, communities are essentially virtual platforms
aggregating web services having similar and complementary
functionalities and communicate with other entities such as UDDI
registries and users using particular protocols. Web services join
communities to increase their utility by having larger market
share and task pool. Community coordinators or master web services
are responsible for community development, managing membership
requests from web services and distributing user tasks among the
community members. Community coordinators try to attract quality
web services and keep the community as stable and productive as
possible to gain better reputation and user satisfaction, which
results in having higher revenue.

\begin{figure*}[!t]
\centerline{\includegraphics[width=15cm]{Figures/archss.eps}}
\caption{Architecture of Web Service communities}
\label{fig_community}
\end{figure*}

@@

\subsection{Task Distribution}

As mentioned in Section \ref{webservice-communities}, communities
are robust service providers with well established market share
and reputation. By maintaining their reputation and performance,
they attract  end users which choose them as service providers to
perform their tasks. The community master is characterized by a
request rate $(R_C)$ from users. Each web service comes with a
given QoS ($QoS_{ws}$) from which the throughput $Th_{ws}$ is
excluded. Throughput is the average rate of tasks a web service
can perform per time unit. Its exclusion from $QoS_{ws}$ allows us
to build our analysis on the particular value of $Th_{ws}$. Thus,
web services perform tasks with an average output quality of
$QoS_{ws}$ and a throughput rate of $Th_{ws}$.

@@

The communities and web services earn revenue by performing tasks.
The total gain is function of quality ($QoS_{ws}$) and throughput
($Th_{ws}$) of tasks being performed. As mentioned in section
\ref{ws_parameters}, $QoS_{ws}$ is obtained by a certain
aggregation function of the parameters considered in Table
\ref{qosws}. We have adopted a linear equal weight average over
all QoS parameters listed in Table \ref{qosws} excluding the
$Throughput$ and $Cost$ parameters. A community has the option to
weigh specific QoS parameters depending on the expectations of
their clients.

@@

%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Case Study: Example 1}
\label{example_1}
\centering
\begin{tabular}{c c c c}
\hline
$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
\hline
1 & 0.8 & 4 & 3.2\\
2 & 0.8 & 5 & 4.0\\
3 & 0.8 & 3 & 2.4\\
\hline
\end{tabular}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Case Study: Example 2}
\label{example_2}
\centering
\begin{tabular}{c c c c}
\hline
$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
\hline
1 & 0.8 & 5 & 4.0\\
2 & 0.7 & 6 & 4.2\\
3 & 0.7 & 4 & 2.8\\
\hline
\end{tabular}
\end{table}

@@

In the first example,  we present the case of a community with
$R_C =10 $, and three web services, each having different
$QoS_{ws}$ and $Th_{ws}$ values as listed in Table
\ref{example_1}. The worth of a community is calculated based on
$Out(C)$ equation (\ref{out_c}) which is the amount of output
being generated by the community. The first table  lists the web
services with their aggregated $QoS_{ws}$ parameters, their task
input rate while working alone, and also their  throughput value
$Th_{ws}$. The second table shows all the possible communities and
their respective worth. The obtained values suggest that
communities having more web services have better gain and output.
However each community needs to  distribute the gain between web
services. Sometimes it is impossible to share the gain between all
web services in a way that no subset of them would individually
gain more if they form their own group. In this example, the value
community of ${ws_1}$ and ${ws_2}$ is 7.2, With ${ws_3}$ joining
the community the worth increases to 8.0. However there is no way
to distribute the value among web services to have  ${ws_1}$ and
${ws_2}$  earning 7.2, and ${ws_3}$ earning at least 2.4, the gain
they could earn before joining the community. This fact makes the
group unstable. In the second  example, shown in Table
\ref{example_2}, we even have situations where a web service
(${ws_3}$) joining a community ($\left\{ws_1,ws_2\right\}$)
decreases the value of community. The reason is, the community is
already full and all tasks are almost being distributed and new
community with bad quality can degrade the average quality of
tasks being done by the community. In both examples, the request
of joining of web service ${ws_3}$ should be rejected by the
community.

%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Case Study: Example 3}
\label{example_3}
\centering
\begin{tabular}{c c c c}
\hline
$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $\text{\emph{Input Task Rate}}$\\
\hline
1 & 0.8 & 10 & 5\\
2 & 0.8 & 20 & 5\\
3 & 0.8 & 30 & 5\\
\hline
\end{tabular}
\end{table}

@@

In coalition-formation games, formation of the coalitions is the
most important aspect. The solutions focus on maximizing the
social welfare. For any coalition structure $\pi$, let
$v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$,
which represents the \emph{social welfare}. The solution concepts
in this area deal with finding the maximum value for the social
welfare over all the possible coalition structures $\pi$. There
are $centralized$ algorithms for this end, but these approaches
are generally NP-complete. The reason is that the number of all
possible partitions of the set $N$ grows exponentially with the
number of players in $N$, and the centralized algorithms need to
iterate through all these partitions.
%These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centralized algorithms, where all the complexity. However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}.
In our model, we propose using a distributed algorithm where each
community master and web service can be a decision maker and
decide for its own good. The aim is to find less complex and
distributed algorithms for forming web services coalitions
\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}.
The distributed merge-and-split algorithm in
\cite{DBLP:journals/igtr/AptW09} suits our application very well.
It keeps splitting and merging coalitions to partitions which are
preferred by all the players inside those coalitions.

@@

Finally, in our last experiment, we compare our work with the work
in \cite{10.1109/TSC.2012.12} which we call it \emph{High
Availability Coalition} method, because of nature of their
community valuation function, which focuses on community
availability as main consideration. Their community formation
model is very different than ours, however we have been very
careful to make the experiment environment as fair and similar as
possible. We limited our maximum community size by 5 in order to
have communities with almost the same size. In their method, they
have used web services as backups rather than active collaborative
players, and they only get task when the first web service in an
ordered chain fails to perform the task. However with recent
advancement in cloud and hardware infrastructures availability is
less of an issue for web services, and web services are highly
available. Part(a) of figure \ref{fig_avail_method} shows our
method performs almost performs tasks successfully with rate of
three times more than \emph{High Availability Coalition} method
because of real cooperative nature and task distribution of our
algorithm. This result shows using web services as backups, and
not as real collabrative players is a huge waste of web service
capability since they have very low chance of getting jobs and its
the primary web service (the first in their coordination chain)
which does most of the work. The average quality of service of
tasks performed is also better since our method considers all
quality of service metrics mentioned in Table \ref{qosws}. Part(c)
shows the availability of community from end user point of view.
The \emph {High Availability Coalition} method almost has 100\%
uptime since they use web services as backups, so the chance of
job failing reduces significantly as community members increase.
In our method we have more chance of fail for each web service,
however with some subsiding, and hiring a few more web service
they can compensate the low chance of failure of web services in
our community.
